---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Blackjack

`Blackjack` is an R package that simulates a multiplayer game of Blackjack between players and a dealer. It implements realistic Blackjack rules such as dealer behavior on soft 17 and bust detection, with players making hit/stand decisions using a simplified strategy.


## Installation

You can install the development version of the package using `devtools`:

```{r, eval = FALSE}
# Install devtools if not already installed
install.packages("devtools")

# Install Blackjack from GitHub
devtools::install_github("MonashARP/game-package-platypuses")
```


## Features

- Simulate 1 or more players in a Blackjack game
- Dealer hits on soft 17 (e.g., Ace + 6)
- Players make decisions using a basic strategy
- Handles busts, ties, and win/loss logic
- Fully documented and unit-tested


## Main Functions

| Function | Description |
|----------|-------------|
| `deck_cards()` | Create and shuffle one or more 52-card decks |
| `deal_hand(deck, n)` | Deal `n` cards from a deck |
| `blackjack_score(hand)` | Calculate Blackjack score for a hand |
| `is_soft_17(hand)` | Check if a hand is a soft 17 |
| `simulate_blackjack_game()` | Simulate a full multiplayer Blackjack game |

---

## Example

```{r}
library(Blackjack)

# Simulate a 2-player game
game <- simulate_blackjack_game(num_players = 2, seed = 123)

# Player 1 results
game$players[[1]]

# Dealer results
game$dealer
```

Example output might look like:

```
$hand
[1] "9♠" "7♣" "3♠"

$score
[1] 19

$result
[1] "Tie!"
```


## Learn More

For full usage examples and gameplay logic, see the package vignette:

```{r, eval=FALSE}
vignette("Blackjack")
```


## Testing

This package includes a full test suite using `testthat`. Run:

```{r}
devtools::test()
```

Tests include:
- Return structure
- Score correctness
- Bust handling
- Dealer soft 17 behavior
- Edge cases like 0 players or 21

---

## Authors

- Vaishnavi Amuda
- Shivesh Palanisamy
- Min Hong

---

## License

MIT License
