---
title: "Blackjack Game"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Blackjack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction of `Blackjack` package
<br> 

This package allows users to calculate the score from a round where the inputs are the cards held by the player and the dealer at the end of the game. It supports scoring individual hands, simulating a full round between a dealer and one or more players, and includes decision-making logic for both players and the dealer—such as hitting, standing, and handling soft 17 scenarios. 

## Usage
```{r, include = FALSE}

#Load the package
library(Blackjack)

#Create a shuffled card deck
deck <- deck_cards()

#Deal a hand
deal_hand(deck_cards()$cards, 2)

#Calculate the score of a hand
blackjack_score(c("A♠", "9♦"))
```


## Example 

### Simulating a round 

The `simulate_blackjack_game()` function plays out a full round of Blackjack for one or more players. It uses all pre-defined helper functions such as `deck_cards()` and `blackjack_score()` to handle deck setup, card dealing, scoring, player decisions, and dealer rules — including the rule of hitting on soft 17.


```{r}
# Simulate a round with 2 players using a set seed to ensure repeatable results
result <- simulate_blackjack_game(num_players = 2, seed = 375)
print(result)
```

### Accessing Player and Dealer Results

You can inspect individual player and dealer outcomes using list indexing:

-  To check the results for Player 1, use:
```{r}
result$players[[1]]
```

You can change the number in players[[x]] to inspect other players (e.g., players[[2]] for Player 2).


- To check the Dealer's hand and score, use:
```{r}
result$dealer
```

### Checking for Soft 17 (Optional Helper)

The helper function `is_soft_17()` checks whether a hand is considered a "soft 17" — that is, a hand totaling 17 that includes an Ace counted as 11. This rule affects whether the dealer should hit or stand during gameplay.

This function is used internally by `simulate_blackjack_game()`, but you can also test hands manually:

```{r}
is_soft_17(c("A♠", "6♦"))     
is_soft_17(c("10♣", "7♦"))    
```


