---
title: "Blackjack Game"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Blackjack Game}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction of `Blackjack` package
<br> 

This package allows users to calculate the score from a round where the inputs are the cards held by the player and the dealer at the end of the game. It supports scoring individual hands, simulating a full round between a dealer and one or more players, and includes decision-making logic for both players and the dealer—such as hitting, standing, and handling soft 17 scenarios. So, users are able to simulate rounds of the classic casino game Blackjack using this package.

## Usage
```{r, eval = FALSE}

#Load the package
library(Blackjack)

#Create a shuffled card deck
deck <- deck_cards()

#Deal a hand
deal_hand(deck_cards()$cards, 2)

#Calculate score in hand
blackjack_score(c("A♠", "9♦"))
```


## Example


### Simulating a round 

The simulate_blackjack_game() function plays out a single round of Blackjack for 1 or more players. It uses all pre-defined helper functions such as deck_cards() and blackjack_score() to handle deck setup, card dealing, scoring, player decisions, and dealer rules—including the rule of hitting on soft 17.

```{r}
# Simulate a round with 2 players using a set seed to ensure repeatable results
result <- simulate_blackjack_game(num_players = 2, seed = 123)
print(result)
```


